Software Citation Principles

### 2016-02-23 sc-principles/software-citation-principles.tex
More domain-specific activities

\textbf{General community/non domain-specific efforts}

@@

NSF/NIH workshops. WSSSPE. JISC reports.

@@

Astronomy: ASCL, AAS journals announcing they will accept software papers in their journals \cite{aas-sofware-papers}. AAS/GitHub
workshop \cite{aas-software-index} dedicated to software citation, indexing and discoverability.

>>>>

\textbf{General community/non domain-specific activities}

@@

Perhaps in recognition of the broad range of research domains struggling with the challenge of better recognizing the role of sofware, a number of community efforts hosted (and sponsored) by funders and agencies in both the US (NSF, NIH, Alfred P Sloan Foundation) and UK (SFTC, JISC) have run a number of workshops with participants from across a range of disciplines.

\asnote{Should also discuss the WSSSPE \cite{wssspe} series of workshops in this section}

@@

One approach to increasing the `citability' of software is to encourage the submission of papers in standard journals describing a piece of research software. While some journals (e.g. F1000Research) have traditionally accepted software submissions, the American Astronomical Society (AAS) have recently annouced they will accept software papers in their journals \cite{aas-sofware-papers}.

In astronomy & astrophysics: ASCL \cite{ascl}, AAS journals  AAS/GitHub
workshop \cite{aas-software-index} dedicated to software citation, indexing and discoverability.

\asnote{Perhaps we should say something here about the potential importance of professional societies and their role in effecting changes in community practice?}
